### 2015-08-31 Irregular-occ/Irregular-occ.tex
.

As explicited in section \ref{Sec: introducao}, there is no consensus on a single model about the region where the irregular satellites were formed. 
%This idea is supported by the

>>>>

As explicited in section \ref{Sec: introducao}, there is no consensus on a single model about the region where the irregular satellites were formed.

Phoebe, the most studied irregular satellite, was identified by \cite{Clark2005} that it has surface material probably of cometary origin. It was also stated by \cite{Johnson2005} that if the porosity of Phoebe would be of about 15\%, Phoebe would have an uncompressed density similar to those of Pluto and Triton.

Triton is a special satellite. Its orbit is retrograde and inclined, but quasi-circular and very close to the planet compared to the irregular ones. Because Triton's orbit is very small and the its precession is not dominated by Solar perturbations, Triton is frequently excluded of the irregular satellites' class, but studied together by many authors \citep{Sheppard2005, Jewitt2007}.

Similar to the irregular satellites, Triton was probably capture in the early Solar System and may have a similar origin as the TNOs \citep{Agnor2006}. Differently, Triton is bigger than the irregular satellites by an order of magnitude and has an atmosphere.
